Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex
starter table python vs others

>>>>

\begin{table}[htbp]
\centering
{\small
\caption{Python (Our Implementation vs. Mutmut vs. CosmicRay)}
\label{tab:table_python2}
\begin{tabularx}{\columnwidth}{l|rrr|rrr|rrr}
\toprule
                 & \mc{3}{c|}{Comby}   & \mc{3}{c|}{MutMut} & \mc{3}{c}{CosmicRay} \\
\textbf{Project} & \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv} 
& \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv} \\ \midrule
keract  & & & & & & & \\
\textbf{Mean} &  XX & XX & XX & XX & XX & XX & XX & XX & XX \\
\textbf{Std.Dev.} &  XX & XX & XX & XX & XX & XX & XX & XX & XX \\
\end{tabularx}
}
\end{table}
